\documentclass{article}

\usepackage{graphicx} % more modern
\usepackage{subfigure} 

\usepackage{natbib}

\usepackage{algorithm}
\usepackage{algorithmic}

\usepackage{hyperref}

\newcommand{\theHalgorithm}{\arabic{algorithm}}

\usepackage{icml2013} 


\icmltitlerunning{}

\begin{document} 

\twocolumn[
\icmltitle{}

\icmlauthor{Yuan Gao}{alex.yuan.gao@it.uu.se}
\icmladdress{Uppsala Univerisity,
            Uppsala, Sweden}

\icmlkeywords{}

\vskip 0.3in
]

\begin{abstract} 
\end{abstract} 

\section{23-09-2017}
I have been trying to access the robot using wireless connect but I did not have much luck.
I send a bugzilla ticket to IT people. Hopefully, they will allow us to do it.
I am not sure what I should do next. Maybe I should setup the environment first

\section{24-09-2017}
Steps of starting the new project.
\begin{itemize}
\item use spr command under terminal
\item run main script under project folder
\item run redcoast.py 
\end{itemize}

\section{02-10-2017}
Three rules

Main principal:
Give when user needs supports.

* Simply wait for long time
1. Incorrect move after long wait time.
2. Completing a row or cloumn
3. Did not use any techniques(how?)

\section{03-10-2017}
For rule 1 

1. First one is strategy * (figure out what strategy can be used for development)
2. Complete the next move * ( this has been modified to be saying it out)
3. no reaction
4. no reaction

For rule 2
1. Correct or not. ( Implemented, not test)
2. show one correct answer on board. * ( this has been modified to be saying it out)

\section{04-10-2017}

#Group3
starDM

#Group4
ourDM

#Group5
AstarDM

#Group10
aStarDM

#Group11
aStarDM

#Group13
newDM

#Group14
myCar

#Group15
aStarDM

#Group16
AStarDM

#Group17
manualDM

#Group18
aStar

#Group19
astarDM

#Group20
manualDM

#Group21
aStarDM   # lack getStartNode

#Group23
aStarDM   # currentNode not understood

#Group27
strategy

#Group30
astarDM

#Group31 * out of bound
ourDM

#Group32
AstarDM

#Group33
a_star * dim is missing

#Group34

#Group35
carReady

\end{itemize}

I have been rewriting the first rule and second rule conbined in red-coast project.
Next step is to write what happens if we know that we have been waiting for long.x

\section{05-10-2017}
In order to balance each category, we need a confirmation of each bahaviour.
Maybe for reward as well

\section{06-10-2017}
We need to fix the system so it only consider conflict as wrong

\section{06-10-2017}
1. Evaluate the infomration sheet
2. Evaluate the explaination of rules
3. Evaluate averange time of completing the nonogram game.



\subsection{}

\nocite{langley00}

\bibliography{example_paper}
\bibliographystyle{icml2013}

\end{document} 


